\vspace{-0.25em}\thetitle

### 2009-07-17 paper.tex
...

The fundamental concept underlying these works is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to points in a vector space;
each dimension of the representation describes some aspect of flow behavior.
The representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix where each row is the linear representation of a flow in the trace.
We restrict our consideration to a particularly natural and powerful class of representations whose coordinates describe the frequencies of flow features.
For example, let there be a dimension for each packet size up to 1500.
Each coordinate indicates the number of packets in a set of flows of that size.
\caps{IP} protocol type, port numbers, and inter-packet intervals can be handled similarly.
% Examples of flow features are the number of packets of a certain size or the use of a particular port number.
% The fundamental premise of this work, and of the sequel, is that the representatives of actual flow behaviors can be understood as being sampled from

The essential observation of this research is that real traffic lies near the union of a small set of low rank subspaces in the representation space.
This allows us to perform a drastic model reduction on traffic data while preserving most characteristics of the original traffic.
Moreover, when observable characteristics of flows are separated from features to be predicted, this model reduction is similar to a classical linear regression, and allows us to very simply predict unseen behavior of flows.
We apply this technique here to directly predict the following characteristics of each flow from observing only a handful of its initial packets:
\begin{enumerate}
  \item the distribution of packets sizes,
  \item the distribution of inter-packet intervals,
  \item the number of packets that will be in the flow.
\end{enumerate}
From these properties, we can indirectly predict many other properties, including the total duration and data volume.
% 
% real-world network traces tend to have approximately low-rank representation matrices despite the potential rank of such matrices being very large.
% Moreover, most flows' vectors lie on only one of a few even lower rank subspaces.
% Moreover, the low-rank subspace near which real traffic lies can be decomposed into subspaces of even lower rank, with almost all flows lying in one of these subspaces.
% Typically, these smaller subspaces are one-dimensional, but in some cases they may have up to a dozen dimensions.

>>>>

The fundamental concept underlying this work is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to vectors, the coordinates of which describe aspects of flow behavior;
the representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix whose rows are the representations of flows in the trace.
We restrict our consideration to a particularly natural and powerful class of representations whose coordinates describe the frequencies of flow features.
For example, the representation can have a dimension for each packet size up to 1500; coordinates in these dimensions indicate the number of packets of each size.
Port numbers, \caps{IP} protocol type, and inter-packet intervals can be handled similarly.
% Examples of flow features are the number of packets of a certain size or the use of a particular port number.
% The fundamental premise of this work, and of the sequel, is that the representatives of actual flow behaviors can be understood as being sampled from

The essential observation of this research is that real traffic lies near the union of a small set of low rank subspaces in the representation space.
This allows us to perform a drastic model reduction on traffic data while preserving most characteristics of the original traffic.
Moreover, when observable characteristics of flows are separated from features to be predicted, this model reduction is similar to a classical linear regression, and allows us to very simply predict unseen behavior of flows.
We apply this technique here to directly predict the following characteristics of each flow from observing only a handful of its initial packets:
\begin{enumerate}
  \item the distribution of packets sizes,
  \item the distribution of inter-packet intervals,
  \item the number of packets that will be in the flow.
\end{enumerate}
From these properties we can indirectly predict many other properties, including the total duration and data volume.
% 
% real-world network traces tend to have approximately low-rank representation matrices despite the potential rank of such matrices being very large.
% Moreover, most flows' vectors lie on only one of a few even lower rank subspaces.
% Moreover, the low-rank subspace near which real traffic lies can be decomposed into subspaces of even lower rank, with almost all flows lying in one of these subspaces.
% Typically, these smaller subspaces are one-dimensional, but in some cases they may have up to a dozen dimensions.
